---
title: "CompareTMVN_R"
author: "Brian Naughton"
date: "04/29/2015"
output: html_document
---

This Rmarkdown file investigates the computational speed of Geweke's algorithm for sampling from a truncated multivariate normal distribution. The example is based on Example from Li & Ghosh (2015).  

```{r}
sessionInfo()
set.seed(327)
```

#### Setup variables:  
```{r}
library(tmvtnorm)
mu = c(0,0,0)
# Sigma = matrix(c(1, .5, .25, 
#                  .5, 1, .5, 
#                  .25, .5, 1), 3, 3, byrow=T)
Sigma = matrix(c(1, .99, .98, 
                 .99, 1, .99, 
                 .98, .99, 1), 3, 3, byrow=T)
lower_bd = c(0,0,-Inf)
upper_bd = c(1,2, Inf)
Rtilde = matrix(c(1, -2, 0,
                  -1, 0, 0,
                  0, 0, 1), 3, 3, byrow=T)
```

#### Time results for Fortran implementation:
 - 10,000 iterations:
```{r}
system.time(rtmvnorm(n=10000, mean=mu, sigma = Sigma, lower = lower_bd, 
                     upper = upper_bd, D = Rtilde, algorithm="gibbs"))
```

 - 100,000 iterations
```{r}
system.time(rtmvnorm(n=100000, mean=mu, sigma = Sigma, lower = lower_bd, 
                     upper = upper_bd, D = Rtilde, algorithm="gibbs"))
```

#### Time results for `R` implementation:  
 - 10,000 iterations:
```{r}
system.time(rtmvnorm(n=10000, mean=mu, sigma = Sigma, lower = lower_bd, 
                     upper = upper_bd, D = Rtilde, algorithm="gibbsR"))
```

 - 100,000 iterations
```{r}
system.time(rtmvnorm(n=100000, mean=mu, sigma = Sigma, lower = lower_bd, 
                     upper = upper_bd, D = Rtilde, algorithm="gibbsR"))
```

### Examine mixing of sampler
#### From traceplot, does it appear that the samples are well mixed?
```{r}
samples = rtmvnorm(n=10000, mean=mu, sigma = Sigma, lower = lower_bd, 
                   upper = upper_bd, D = Rtilde, algorithm="gibbs")
plot(samples[,1], type='l', xlab='Iteration', ylab='w_1')
plot(samples[,2], type='l', xlab='Iteration', ylab='w_2')
plot(samples[,3], type='l', xlab='Iteration', ylab='w_3')
```
  
#### What do the marginal distributions look like?
```{r}
hist(samples[,1], breaks=50, xlab="w", ylab="", main="Histogram of w_1")
hist(samples[,2], breaks=50, xlab="w", ylab="", main="Histogram of w_2")
hist(samples[,3], breaks=50, xlab="w", ylab="", main="Histogram of w_3")
```

#### How correlated are samples from the Gibbs sampler?
```{r}
acf(samples[,1], main="Autocorrelations for w_1")
acf(samples[,2], main="Autocorrelations for w_2")
acf(samples[,3], main="Autocorrelations for w_3")
```